---
title: "Assignment 8"
author: "Wiktor Rorat"
format: html
editor: visual
embed-resources: true
---

```{r}
#| warning: false
library(dplyr)
library(ggplot2)
library(ggstance)
```

I chose to remake the challenger disaster graph. I was able to find the dataset in a repository:

<https://archive.ics.uci.edu/dataset/92/challenger+usa+space+shuttle+o+ring>

```{r}
#| warning: false
file <- read.csv2("o-ring-erosion-or-blowby.data", header = FALSE, sep=" ", col.names = c("num_O_rings", "num_thermal_distress", "launch_temp", "leak_check_pressure", "temporal_order"))

# converting fahrenheit to celsius
file$launch_temp = (file$launch_temp - 32) * (5/9)
```

```{r}
#| warning: false
ggplot(file, aes(x=launch_temp, y=factor(num_thermal_distress)))+
  geom_point(color="darkred", shape=2, position=position_dodge2v(height = 0.1))+
  geom_vline(xintercept=-3.33, linetype="twodash", alpha=0.9)+
  geom_vline(xintercept=-1.66, linetype="twodash", alpha=0.9)+
  ggtitle("O-rings damage during previous launches")+
  ylab("O-rings damaged (out of 6)")+
  xlab("Temperature at launch (°C)")+
  geom_segment(aes(x = 3, y = 0.75, xend = 0, yend = 0.75),
    arrow = arrow(), size=0.05) +
  annotate("text", label = "predicted temperature next launch",x=6, y=1)+
  theme_minimal()
```

Changing y-axis values into objects of class "factor" removes non-integer ticks from the axis. I have not found a satisfactory way to help with points overlap; the points should dodge each other vertically, since the number of O-rings number is an integer. I used a library to achieve that, but the results are not perfect.
